Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-16 paper.tex
Terms that can be computed from the experimental data
Drag coefficients are slightly higher

Results from the terms available (i.e. excluding $\partial / \partial x$) from
the right hand sides of Equations~\ref{eq:momentum} and \ref{eq:K-full} are
plotted in Figures~\ref{fig:mom-bar-graph} and \ref{fig:K-bar-graph},
respectively. Derivatives were computed using a second order finite difference
scheme, with central differencing for interior points, and inward facing schemes
for the boundaries. A weighted average for each term was then calculated based
on the grid spacing. We note that similar to \cite{Bachant2015-JoT}, the
vertical advection at this point in the wake is the dominant contributor to
positive wake recovery, caused by the unique vortex pattern created by the blade
tips and wakes.

@@

Transport due to cross-stream advection appears to become more negative at
higher $Re$. This could be a consequence of increasing free surface deformation
(higher $Fr$), which then decreases the effective flow cross-sectional area
downstream of the turbine, forcing more flow to accelerate around the sides of
the turbine. Note that we also see higher drag coefficients at higher $Re$
(potentially for the same reason), which also helps explain larger negative
values of cross-stream advection.

>>>>

Results from the terms that can be computed from the experimental data (i.e.
excluding $\partial / \partial x$) from the right hand sides of
Equations~\ref{eq:momentum} and \ref{eq:K-full} are plotted in
Figures~\ref{fig:mom-bar-graph} and \ref{fig:K-bar-graph}, respectively.
Derivatives were computed using a second order finite difference scheme, with
central differencing for interior points, and inward facing schemes for the
boundaries. A weighted average for each term was then calculated based on the
grid spacing. We note that similar to \cite{Bachant2015-JoT}, the vertical
advection at this point in the wake is the dominant contributor to positive wake
recovery, caused by the unique vortex pattern created by the blade tips and
wakes.

@@

Transport due to cross-stream advection appears to become more negative at
higher $Re$. This could be a consequence of increasing free surface deformation
(higher $Fr$), which then decreases the effective flow cross-sectional area
downstream of the turbine, forcing more flow to accelerate around the sides of
the turbine. Note that we also see slightly higher drag coefficients at higher
$Re$ (potentially for the same reason), which also helps explain larger negative
values of cross-stream advection.
